---
title: "Interactive Application"
author: "Aarushi Agarwal"
date: "9/2/2020"
output: pdf_document
---

```{r setup, include=FALSE}

if(!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, shiny,reshape, ggplot, ggmap,corrplot,ggplot2,matrixStats,sf,deplyr,tidyr,data.table,maps,htmltools,leaflet,caret, DMwr)
#search()

```

```{r}
housing.df <- read.csv(file="Housing_2020.csv", header=TRUE, sep=",")


#Data Pre Process
#Note: Not removing outliers because this is a shiny app to help user explore different kind of preperty, even the high priced ones
housing.clean.df<-subset(housing.df,housing.df$PROPERTY.TYPE=="Single Family Residential" | housing.df$PROPERTY.TYPE=="Townhouse" )
#removing  null values for year and  baths;total count =3
housing.clean.df<-housing.clean.df[!is.na( housing.clean.df$YEAR.BUILT),]
housing.clean.df<-housing.clean.df[!is.na( housing.clean.df$BATHS),]
#lapply(housing.clean.df,function(x) { length(which(is.na(x)))})
#replacing nulls with median for lot size as the mean would be biased because of outliers
housing.clean.df$LOT.SIZE[is.na(housing.clean.df$LOT.SIZE)]<-median(housing.clean.df$LOT.SIZE)
#lapply(housing.clean.df,function(x) { length(which(is.na(x)))})
#summary(housing.clean.df)

```



```{r}

# Adding a column for displaying as a label for maps
housing.clean.df$label<-paste("Square Feet: ",housing.clean.df$SQUARE.FEET,"| Lot Size:  ", housing.clean.df$LOT.SIZE,"| Year Built: ", housing.clean.df$YEAR.BUILT)
# tab2 dataframe created for generating data table for Tab2
tab2<-aggregate(housing.clean.df$PRICE,list(housing.clean.df$ZIP.OR.POSTAL.CODE, housing.clean.df$PROPERTY.TYPE),median)
tab2_wide<-spread(tab2, Group.2,x)
names(tab2_wide)[names(tab2_wide)=="Group.1"]<-"ZIPCODE"
tab2_ordered<-tab2_wide[with(tab2_wide,order(-tab2_wide$`Single Family Residential`)),]

tab2_dt<-setDT(tab2_ordered, keep.rownames=FALSE)

```


Tab 1: A histogram that shows the distribution of home prices in a zip code.
Include a drop-down input list that allows a user to choose one or multiple zip
codes at a time. 
```{r}


ui <- fluidPage(
  titlePanel("A histogram that shows the distribution of home prices in a zip code"),
  selectInput(inputId = "zipcode",label = "Select Zipcode:",choices=housing.df$ZIP.OR.POSTAL.CODE, multiple = TRUE, selected = 75219 ),
  
  plotOutput(outputId = "hist")
)
server <- function(input, output, session) {

      output$hist <- renderPlot({
        prices.df<-subset(housing.df,housing.df$ZIP.OR.POSTAL.CODE==input$zipcode)
       ggplot( prices.df, aes(x =PRICE) )+
       geom_histogram( color = "purple", fill="pink")+ggtitle("Histogram of Price Distribution for selected Zipcodes")
    
})
}
shinyApp(ui = ui, server = server)

```

Tab2: A table that shows the median home price by zip code (row) and property
type (column). Sort the table by descending order of “Single Family Residential”
home price. 

```{r}
ui <- fluidPage(
  titlePanel("Median Prices based on ZipCodes and Property Type"),
  
  
  tableOutput(outputId = "table")
)
server <- function(input, output, session) {

      output$table <- renderTable({
      
      
      tab2_dt
})
}
shinyApp(ui = ui, server = server)
```
Tab 3: A boxplot for a specific (number of) beds, (number of) baths, square feet,
lot size, and year built combination. For each of the above features, include a
slider input.

```{r}
ui <- fluidPage(
  titlePanel("A boxplot for a specific (number of) beds, (number of) baths, square feet,
lot size, and year built combination."),
  sidebarLayout(
    sidebarPanel(
      

       sliderInput(inputId = "beds",
                   label = "Select no. of Beds:",
                   min = 0, max = 8,
                   value = 0),
       sliderInput(inputId = "baths",
                   label = "Select no. of Baths:",
                   min = 1, max = 9,
                   value = 1, step=0.5),
       sliderInput(inputId = "sqFeet",
                   label = "Select Square Feet:",
                   min = 528, max = 27075,
                   value = 528),
       sliderInput(inputId = "lot",
                   label = "Select Lot Size:",
                   min = 44, max = 5227200,
                   value = 44),
       sliderInput(inputId = "year",
                   label = "Select Year Built:",
                   min = 1868, max = 2021,
                   value = 1868),

    ),
    mainPanel(
       
       plotOutput(outputId = "boxplot")
    )
       
  )
     
 )

 
 server <- function(input, output) {

   output$boxplot<-renderPlot ({ 
     pricesBox.df<-subset(housing.clean.df,housing.clean.df$BEDS==input$beds | housing.clean.df$BATHS==input$baths |
                            housing.clean.df$SQUARE.FEET ==input$sqFeet | housing.clean.df$LOT.SIZE==input$lot |
                            housing.clean.df$YEAR.BUILT==input$year)
    ggplot(pricesBox.df) +
  geom_boxplot(aes(, y =PRICE), 
               fill = "gold1", outlier.color = "firebrick2") + 
  xlab("PRICE") + ylab("Values")+ggtitle("BoxPlot for Price")
  
   })
 }

 # Create a Shiny app object ----
 shinyApp(ui = ui, server = server)


```

Tab 4: A map that shows the location of the home. When a user hovers over a
particular property, s/he should be able to see basic information about the
property, such as square feet, lot size, year built, etc.
```{r}


ui <- fluidPage(
  titlePanel("A map that shows the locations of the home"),
  leafletOutput("map")
)
server <- function(input, output) {
  output$map<- renderLeaflet({
leaflet(housing.clean.df) %>% addTiles() %>% addCircleMarkers( radius=0.5,color = ~"yellow", fill = TRUE, label = ~ label) 

})
}
shinyApp(ui = ui, server = server)


```






